### 2020-10-11 Analysis/Code/Paper.Rmd
Corrections

In his book “Economics for the Common Good” Jean Tirole proclaims the economy we live in to be governed by “Economics of Attention” [-@Tirole17]. A simple search for wine glasses on Amazon.com results in more than 5,000 options, leading to a choice problem that is virtually impossible to solve satisfactory without guidance. Such guidance is provided by different types of recommendation systems. Many marketplaces or third party websites allow consumers to review products and services that they purchased, and aggregate these reviews into a rating, greatly facilitating the comparison between the alternatives. These ratings are often given a simple graphical representation; for example, a number of stars between 0 and 5 is a common way to split the alternatives into *review tiers*. Such review tiers are used to review household items (Amazon), movies (IMDb), restaurants (Yelp), doctors (RateMDs), and many other products and services. Both an extensive literature in marketing, and anecdotal evidence from these markets, suggest that good reviews are at the very least important for the success of the business. Not surprisingly, firms assume an active approach to managing their reviews. Firms solicit reviews from their clients, publicly respond to reviews, and even leave fake reviews for themselves or their competitors.

In this paper I study a novel form of review management. I show that firms can use discounting in order to facilitate *transitions* between review tiers. Imagine a product that is several good reviews short of obtaining an additional star. I ask: would it be profitable for such a product to run a price promotion?  With a help of a stylized model, I identify two effects that influence this decision: the *selection* effect and the *variance* effect. Customers who purchase the good on a discount are likely to be different from the ones who pay the full price, and could potentially leave different reviews. If such reviews tend to be more favorable, then the induced positive selection effect creates incentives for the product to go on discount. Whether the selection effect is positive or negative is an empirical question, and I answer this question with my data. The variance effect reflects the idea that a product that is close to a transition is willing to gamble on upgrading its review tier. Extra positive reviews catapult it to the next review bin, which promises higher sales, while a few negative reviews would not affect its review status and sales much. While extra variance is good for products that are on the verge of a tier upgrade, it could be harmful for products that are close to sliding one review tier down. Fearing to lose that precious star, such products would prefer to delay running a price promotion, unless the selection effect is positive and strong.

@@

To learn more about the relative contributions of the variance and the selection effects to the observed behavior, I estimate the review part of my structural model. I estimate the effect of discounts on the probabilities to leave positive and negative reviews. I find no evidence that the selection effect is positive on Steam, meaning that, on average, reviews left during a price promotion are not more favorable than the ones left outside of a price promotion. Thus, I attribute firms' behavior to the variance effect. While this effect is hard to test directly, I provide some further indirect tests of its impact on the discounting behavior around review tier transitions. I estimate the size of the selection effect at the product level, and “control” for it in my regressions of discounts on proximities to transition. I find that, in the absence of the selection effect, products that are close to a review downgrade are significantly less likely to discount, which is consistent with the idea that the variance effect is negative for such products. I also provide novel evidence that consumers who buy the product during a price promotion are more likely to leave a review, which speaks to the mechanism through which “variance” is created by a discount.

## Literature Review

While some of my findings are new and interesting on their own, others are best measured against the literatures in economics and marketing that I contribute to. The oldest of these is the literature investigating the impact of online consumer reviews on sales. An extensive review of the studies focusing on this topic and their meta-analysis is provided, for example, by @Floyd14. 
<!-- Researchers have analyzed multiple online platforms, selling different products and employing different review systems, and produced, overall, conflicting evidence on whether reviews improve sales, and if so, through which channels. The major identification challenge stems from the fact that better reviews might simply be manifestations of consumer preferences for certain products, or reflect higher quality of the underlying products. As preferences and quality are unobserved and, in general, fluid, researchers have struggled to come up with convincing identification strategies. -->
In a seminal contribution in this literature, @ChevalierMayzlin06 uses a difference-in-differences approach, exploiting the differences in reviews for the same books across Amazon.com and Barnesandnoble.com, to argue that better reviews causally improve sales. A similar approach applied to the same market was recently used by @ReimersWaldfogel20, who reaffirm the importance of reviews for sales of books and quantify the welfare implications of the informational content of consumer reviews. @ZhuZhang10 exploit differences between two different video games consoles rather than websites, and find that review ratings matter only for less popular games.

For identification, the difference-in-differences approach relies on the existence of several comparable platforms, and assumes that the unobserved platform-specific tastes
for those platforms are fixed. Another approach to identification exploits the rounding of the review data that platforms use to produce simple visual review labels. For example, Yelp.com, a popular restaurant comparison service, assigns 4 stars to restaurants that have an average review score between 4 and 4.24 (out of 5), but 4.5 stars to restaurants with an average score between 4.25 and 4.74.  @AndersonMagruder12 and @Luca16 develop a regression discontinuity approach exploiting this rounding to show that an additional half-star on Yelp.com increases restaurants' traffic and revenue. In studies relying on a discontinuity for identification, it is crucial that assignment around thresholds is as good as random. Unlike the settings in which the variable that is measured against the cutoff is realized once (a student takes the test once, and either earns an “A” or a “B”), products carry their review scores from day to day. If one product is slightly below the cutoff and has 4 stars, and another product is slightly above the cutoff, why would the former not try to do something to cross the cutoff, especially if better review bins are more lucrative? My paper asks precisely that question, and shows that such concerns are well-founded. However, I do not study the implications of such behavior for a regression discontinuity approach used in the aforementioned papers.

@SorokinStevens20 raises other concerns about the validity of the regression discontinuity approach in studying the causal effect of reviews on outcomes. To my knowledge, it was the first paper to use Steam as the object of its analysis. In the absence of direct sales data, @SorokinStevens20 uses a particular regression specification that extracts the information on sales from the video games' usage data. I inherit the data from that paper, but confront the absence of sales data in a more hands-on way. I make assumptions about the gaming patterns of the users of the games in my sample, and formulate a structural model of the data generating process. With the help of that model, I manage to extract information on product sales from usage data only. I also compare the estimates of the structural model with the ones obtained by its simpler regression analog, which happen to be quite similar. The last improvement of the present study over @SorokinStevens20 is that I employ all the relevant review tiers present on Steam, while in earlier work the regression discontinuity approach dictated the focus on a certain subset of review labels.

@@

Direct ways of managing online reputation discussed above, however, are not the only avenues through which businesses can affect their reviews. Reviews are left by customers, and the happier they are, the better reviews they should leave, at least in principle. Another strand of literature is studying whether price promotions have an effect on firms' online reputation. In a seminal study, @ByersEtAl12 documents that restaurants receive substantially worse reviews after running a price promotion through Groupon, a promotion service. In other words, @ByersEtAl12 documents a negative selection effect on Yelp. It presents evidence that customers attracted by a promotion are different from regular customers, and that they are more likely to be trying out a new restaurant or cuisine while using the Groupon voucher. This difference can explain the reasons behind the dissatisfaction of the Groupon customers. @Li16 confirms the finding in the same setting, but finds that restaurants with fewer and worse reviews can actually benefit from participating in a Groupon promotion. There are a couple of other studies that dispute the negativity of the selection effect. @ZhuEtAl19 shows that customers who received a discount leave more positive, albeit less informative, reviews. In an experimental study on Ebay, @CabralLi15 also finds that offering a rebate for leaving (any) review significantly decreased the likelihood of negative feedback, and it provides evidence that this is due to reciprocity on the side of the clients, rather than the differences between customers buying with a rebate and without it. My study contributes to this debate by documenting the absence of a positive selection effect in a new market. Additionally, my paper is the first to focus on discrete changes in review tiers that follow the discounts, instead of studying the continuous effect of a discount on the review score.

Based on its findings, @ByersEtAl12 cautions businesses against running price promotions in an attempt to poach new customers and improve their online reputation. To the extent that managers and scholars perceive promotions to be an effective way of managing reputation, this finding presents a puzzle. A similar puzzle is encountered by @Zegners17, which argues that less-known authors of eBooks on a crowded online marketplace are more likely to give their books out for free in order to build reputation and escape the "zero reviews trap". While the idea is intuitive, the findings are that products employing free pricing are more likely to solicit *negative* feedback when sold for free, which somewhat undermines the strategy. I provide a novel mechanism--- the variance effect---that could explain the prevalence of price promotions when the selection effect of reviews is negative. The variance effect would explain the behavior observed in @Zegners17 as follows: if a  product with no reviews is already doomed, it would find it profitable to sell for free even if the probability to solicit favorable reviews is small. After all, sales can not fall below zero, but the upside of accumulating some positive reviews and escaping the trap is substantial.

The rest of this paper is organized as follows. Section \ref{dataSection} describes the institutional setting and the data I use. Section \ref{demandSection} develops and estimates the structural model of demand and gaming activity on Steam. The technical nature of the material in this section contributes greatly to its size, but goal of this section is simply to quantify the importance of different review tiers on sales, and to show that discounts are effective in attracting new customers. The main findings are described in  Section \ref{descriptiveEvidence}. It opens with a stylized model of discounting for a product close to a review tier transition, and introduces the selection and the variance effects. The section proceeds by establishing that such discounting behavior takes place in the data. Section \ref{selectionEffect} supplements the demand model from Section \ref{demandSection} by a model of reviewing activity, and estimates its parameters in order to quantify the relative contributions of the selection and the variance effect to the observed patterns of discounting around review transitions. Section \ref{conclusion} concludes.

@@

Steam is arguably the largest online marketplace for selling computer games in the world. Founded in 2003, in 2013 it was responsible for about 75\% of PC games sold online globally [@steamBloomberg], and in 2017 it has earned around US\$4.3 billion, with an estimated market share of 18\% in the entire market for PC games [@psgames]. Given an ongoing unprecedented growth in the size of the video games' market [\$43.4 billion 
in 2018, about the size of the U.S. film industry, @videoGamesMarket] and the increasing share of online sales in this market [83\% in 2018, compared to 20\% in 2009, @steamNPD[], Steam is a major player in an increasingly more important industry. Thus, this marketplace is not merely a laboratory for studies hoping to extrapolate the findings to other more well-known platforms, but is an important digital market to be studied in its own right.

Any user who has a copy of a game on Steam can leave a review for that game. Starting from late 2016, by default, Steam only uses reviews left by customers who have *purchased* the game in its review score calculation, excluding reviews left by customers who had obtained a key to activate the game through other channels (directly from the developer, or by purchasing the code from a different retailer). This distinguishes Steam from some other platforms studied in the literature, notably Yelp and TripAdvisor, where any user can leave a review (and, to a certain extent, Amazon, where non-verified users can also leave reviews). This gives me confidence in the authenticity of most reviews. This confidence is further backed by the importance of Steam to game developers and publishers, and Steam's history of monitoring the platform for fraudulent activity and excluding unscrupulous actors. With such high stakes, and a non-negligible risk of being caught, there are good reasons to expect the developers to behave scrupulously.

A review consists of a binary grade, "thumbs up" or "thumbs down", and review's text. A *review score* is defined as the fraction of positive reviews among all reviews a game has, provided it has at least 10 reviews. Based on the score, Steam assigns *review labels*, or bins, to each game. These labels\footnote{There are labels worse than “Negative”, but they are rare, so I bin all of them into “Negative”} and the mapping rules are summarized in Table \ref{tab:ReviewBinsTable}. For example, a game with 7 positive and 2 negative reviews would have neither a review score, nor a label, but an extra positive review would promote it to the “Positive” bin.

@@

Steam's homepage welcomes customers with a selection of featured games, that could include new games, popular games that are currently on a discount, games that have recently released a major update, etc. [@steamVisibility]. A customer could either click on the games already presented to her, or browse one of the categories that Steam offers. Available categories are based on games' characteristics such as performance (e.g., “Top Sellers”, “New Releases”), genre (e.g, “Racing”, "Anime", “Simulation”), or technical characteristics (VR or controller support). Games within a category are organized into a list, with an example session presented in Figure \ref{steamStore}. From that list the user can get some basic information about each title, such as its name, price, and if the game is currently on a discount. Importantly, if the user hovers her cursor over a game, she could further see the review label of the game and the number of reviews the game has. I use this feature of Steam's store to rationalize why later in the analysis I choose to focus on the review labels as my main explanatory review variables, rather than, say, the review score or the review texts. Granted, informative review texts could be important for purchase decisions [@ChevalierMayzlin06], but on Steam, in order to gain access to such information, a customer should be willing to click on the game in the first place. @deLanghe15 reports that consumers place an unreasonably high weight on the star rating of products\footnote{The title of the present study is an omage to the masterfuly chosen title of \citet{deLanghe15}.}. Thus, I conjecture that games with better review labels will, other things equal, attract more customers, and lead to more sales. Crucially, according to Steam's documentation, all review labels better than “Negative“ have a very similar contribution to visibility on the platform, which means, for example, that games are not ordered by their review labels when the customer is browsing different categories [-@steamVisibility2]. Therefore, any effect of the review labels on, say sales, should come through the perceived quality differences between different bins, rather than some mechanical visibility differences. As an illustration, note that the first game in the list depicted in Figure \ref{steamStore} has “Mixed” reviews.

@@

Descriptive information on any game, that I will refer to as “static”, such as its title, developer, release date, etc., are readily available from Steam, and this information is also present on SteamDB. More importantly, Steam Database offers a daily time series of prices and player activity for each game on Steam. In principle, the pricing information could be obtained by a repeated scraping of the store. However, the player activity information is not trivial to obtain, as Steam does not directly reveal such data, let alone the data on sales of different titles. The creators of SteamDB have declined to explain their collection method, but their reputation in the gaming community most certainly implies that they are doing the best they can. The resulting variable that SteamDB offers, that I will refer to as the *player count*, measures the maximum number of concurrent player for each game on a daily basis. In other words, if on a particular day 10 people play the game every hour, except noon, when 13 people play the game simultaneously, then the recorded player count for this game on that day will be 13. The price and the player count time series are the major “dynamic” variables used in the analysis. The last dynamic variable, namely the review score of each game, is obtained by scraping the reviews directly from Steam, and reverse engineering the evolution of the review score.

@@

The final sample includes `r info[, .N]` games which I observe for `r panel[, max(age), by = ID][, round(mean(V1))]` days each, on average. The main variables in the analysis are the aforementioned dynamic variables: player count, price, and review score. An example observation from the sample is given in Figure \ref{exampleGame}. For the majority of the games in the sample, the player count is the highest around the release date, and then it quickly fades away and oscillates around a smaller level. The player count also jumps when a discount is given, reflecting the influx of new players. Games differ a lot in their sizes, as is evident from Figure \ref{sampleSizeHist}.

```{r sample-size-hist-vert, include=FALSE, fig_height = 5}
# for beamer
ggarrange(p1, p2, ncol = 1, nrow = 2, align = "h")
```

As the goal of the paper is to understand if firms use pricing tools in order to improve their online reputation, a detailed overview of pricing and review variables is in order. A representative game in the sample never changes its price, but instead occasionally goes on discounts, slowly increasing their magnitude as the game ages. There are
`r panel[discount==F, diff(price), by = ID][V1>0, .N]` incidents of price change in the data, compared to 
`r panel[discNew==T, .N]` discounts. Steam has a number of rules that regulate price promotions on its platform. A game can have a launch discount, but, otherwise, it has to wait for two months since the release before changing its price or giving a discount. A game can not go on discounts too frequently, and has to wait between four to six weeks
after a price promotion to be able to run a new one. The duration of a custom discount is restricted to be at least one full day, and at most two weeks. Besides these custom discounts, that are fully managed by the firms, Steam has a series of curated discounts, when the platform invites selected titles to go on a discount. As @steamDiscounting explains it, “while there aren't strict rules, as a base guideline we tend to focus on the top 10-20% selling games on Steam that are positively reviewed and have otherwise proven to be successful”. Curated promotions are featured prominently on Steam's main page, and, arguably, lead to more visibility and sales for the participating titles than custom discounts, which also contribute to visibility, but typically do not get the front-page promotional slots. An important type of curated discounts are the so-called “Seasonal Sales”--big platform-wide events that take place about four times a year around major holidays. Figure \ref{seasonalSalesPeriods} (in the Appendix) shows that the biggest sales take place in Winter (Christmas and New Year) and Summer (July 4), but there are also significant discounts in the Fall (Halloween and Thanksgiving). Around `r  round(panel[discSeason==T & discNew == T, .N]/panel[discNew==T, .N]*100)`% of discounts in the sample go live during a Seasonal Sale. Thus, firms have significant agency when it comes to running price promotions, but platform regulations and platform-wide discounts are important determinants of firms' decision to discount.

@@

The path of the review score of a typical game is quite different from its price history, in that the review score tends to settle quickly. Recall that the review score is just the fraction of positive reviews among all reviews, so the law of large number implies that this ratio crystallizes as more reviews flow in. Second plot in Figure \ref{reviewDescriptivePlots} shows that games tend to receive half of the reviews they have at the age of 180 days in their first month after the release. On average across games, the standard deviation of the review score is just `r round(panel[, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)`  (out of one hundred), with a split of `r round(panel[age <= 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` in the first thirty days and `r round(panel[age > 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` after that. Given how little the review score changes after the first month, the distribution of games by bins at the age of 180 days, depicted in Figure \ref{reviewDescriptivePlots}, should be representative of the situation at other ages.

```{r}
transitions <- panel[, .(t, neg=c(NA, diff(negative)),
                    mix=c(NA, diff(mixed)),
                    mpos=c(NA, diff(mPositive)),
                    pos=c(NA, diff(realPositive)),
                    vPos=c(NA, diff(vPositive)),
                    ovPos=c(NA, diff(ovPositive)),
                    negative, mixed, mPositive, realPositive,
                    vPositive, ovPositive), by=ID]
transitions <- transitions[neg ==-1 | mix ==-1 | 
                           mpos == -1 | pos == -1 | 
                           vPos == -1 | ovPos == -1, ]
transitions[neg==-1, origin := "Negative"]
transitions[mix==-1, origin := "Mixed"]
transitions[mpos==-1, origin := "M. Positive"]
transitions[pos==-1, origin := "Positive"]
transitions[vPos==-1, origin := "V. Positive"]
transitions[ovPos==-1, origin := "Ov. Positive"]
transitions[, origin := factor(origin, 
                               levels = labls[-1],
                               labels = labls[-1],
                               ordered = T)]
setkey(transitions, ID, t)
transitions[, trID := (1:length(t)), by = ID]
setkey(transitions, ID, t, trID)
# separate good transitions from bad transitions
transitions[, goodTr := F]
transitions[neg==-1 | (mix==-1 & neg!=1) | (mpos == -1 & mix != 1 & neg!= 1) |
            (pos==-1 & (vPos==1 | ovPos==1)) | (vPos==-1 & ovPos == 1), goodTr := T]

transitions[, dur := shift(t,-1) - t, by = ID]
```

>>>>

In his book “Economics for the Common Good” Jean Tirole proclaims the economy we live in to be governed by “Economics of Attention” [-@Tirole17, p.379]. A simple search for wine glasses on Amazon.com results in more than 5,000 options, leading to a choice problem that is virtually impossible to solve satisfactory without guidance. Such guidance is now routinly provided by different types of recommendation systems. Many marketplaces or third party websites allow consumers to review products and services that they purchased, and then aggregate these reviews into a rating, greatly facilitating the comparison between alternatives. These ratings are often given a simple graphical representation; for example, a number of stars between 0 and 5 is a common way to split the alternatives into *review tiers*. Such review tiers are used to review household items (Amazon), movies (IMDb), restaurants (Yelp), doctors (RateMDs), and many other products and services. Both an extensive literature in marketing, and anecdotal evidence from these markets, suggest that good reviews important, if not crucial, for the success of the business. Not surprisingly, firms assume an active approach to managing their reviews. Firms solicit reviews from their clients, publicly respond to reviews, and even leave fake reviews for themselves or their competitors.

In this paper I study a novel form of review management. I show that firms can use discounting in order to facilitate *transitions* between review tiers. Imagine a product that is several good reviews short of obtaining an additional star. I ask: would it be profitable for such a product to run a price promotion?  With a help of a stylized model, I identify two effects that influence this decision: the *selection* effect and the *variance* effect. Customers who purchase the good on a discount are likely to be different from the ones who pay the full price, and could potentially leave different reviews. If such reviews tend to be more favorable, then the induced positive selection effect creates incentives for the product to go on discount, as new customers are likely to leave positive reviews and help the product advance to the next review tier.  Whether the selection effect is positive or negative is an empirical question, and I answer this question with my data. The variance effect reflects the idea that a product that is close to a transition is willing to gamble on upgrading its review tier. Extra positive reviews catapult it to the next review bin, which promises higher sales, while a few negative reviews might not affect its review status---and, therefore, sales---by much. While extra variance is good for products that are on the verge of a tier upgrade, it could be harmful for products that are close to sliding one review tier down. Fearing to lose that precious star, such products would prefer to delay running a price promotion, unless the selection effect is positive and strong.

@@

My structural model provides further insight into the relative contributions of the variance and the selection effects to the observed behavior. I estimate the effect of discounts on the probabilities to leave positive and negative reviews. I find no evidence that the selection effect is positive on Steam, meaning that, on average, reviews left during a price promotion are not more favorable than the ones left outside of a price promotion. Thus, I attribute firms' behavior to the variance effect. While this effect is harder to test directly, I provide some  indirect tests of its impact on the discounting behavior around review tier transitions. I estimate the size of the selection effect at the product level, and “control” for it in my regressions of discounts on proximities to transition. I find that, in the absence of the selection effect, products that are close to a review downgrade are significantly less likely to discount, which is consistent with the idea that the variance effect is negative for such products. I also provide novel evidence that consumers who buy the product during a price promotion are more likely to leave a review, which speaks to the mechanism through which “variance” is created by a discount.

While some of my findings are new and interesting on their own, others are best measured against the literatures in economics and marketing that I contribute to. The oldest of these is the literature investigating the impact of online consumer reviews on sales. An extensive review of the studies focusing on this topic and their meta-analysis is provided, for example, by @Floyd14. In a seminal contribution to this literature, @ChevalierMayzlin06 uses a difference-in-differences approach, exploiting the differences in reviews for the same books across Amazon.com and Barnesandnoble.com, to argue that better reviews causally improve sales. A similar approach applied to the same market was recently used by @ReimersWaldfogel20, who reaffirm the importance of reviews for sales of books and quantify the welfare implications of the informational content of consumer reviews. @ZhuZhang10 exploit differences between two different video games consoles rather than websites, and find that review ratings matter only for less popular games.

For identification, the difference-in-differences approach relies on the existence of several comparable platforms, and assumes that the unobserved platform-specific tastes
for those platforms are fixed. Another approach to identification exploits the rounding of the review data that platforms use to produce simple visual review labels. For example, Yelp.com, a popular restaurant comparison service, assigns 4 stars to restaurants that have an average review score between 4 and 4.24 (out of 5), but 4.5 stars to restaurants with an average score between 4.25 and 4.74.  @AndersonMagruder12 and @Luca16 develop a regression discontinuity approach exploiting this rounding to show that an additional half-star on Yelp.com increases restaurants' traffic and revenue. In studies relying on a discontinuity for identification, it is crucial that assignment around thresholds is as good as random. Unlike the settings in which the variable that is measured against the cutoff is realized once (a student takes the test once, and either earns an “A” or a “B”), review scores of products on review platforms are moving slowly and are tested against the threshold on a daily basis. If a product is slightly below the cutoff and has 4 stars, why would it not try to do something to cross the cutoff, especially if better review bins are more lucrative? My paper asks precisely that question, and shows that such concerns are well-founded. I do not study the implications of such behavior for a regression discontinuity approach used in the aforementioned papers, but my findings could inform further inquiry into the subject.

@SorokinStevens20 raises other concerns about the validity of the regression discontinuity approach in studying the causal effect of reviews on outcomes. To my knowledge, it was the first paper to use Steam as the object of its analysis. In the absence of direct sales data, @SorokinStevens20 uses a particular regression specification that extracts the information on sales from video games' usage data. I inherit the data from that paper, but confront the absence of sales data in a new way. I make assumptions about the gaming patterns for the games in my sample, and formulate a structural model of the data generating process. With the help of this model, I manage to extract information on product sales from usage data. I compare the estimates of the structural model with the ones obtained by its simpler regression analog, and find important similartities and dissimilarities. The last improvement of the present study over @SorokinStevens20 is that I employ all the relevant review tiers present on Steam, while in earlier work the regression discontinuity approach dictated the focus on a certain subset of review labels.

@@

Direct ways of managing online reputation discussed above, however, are not the only avenues through which businesses can affect their reviews. Reviews are left by customers, and the happier they are, the better reviews they should leave, at least in principle. Another strand of literature is studying whether price promotions have an effect on firms' online reputation. In a seminal study, @ByersEtAl12 documents that restaurants receive substantially worse reviews after running a price promotion through Groupon, a promotion service. In other words, @ByersEtAl12 documents a negative selection effect on Yelp. It presents evidence that customers attracted by a promotion are different from regular customers, and that they are more likely to be trying out a new restaurant or cuisine while using the Groupon voucher. This difference can explain the reasons behind the dissatisfaction of the Groupon customers. @Li16 confirms the finding in the same setting, but finds that restaurants with fewer and worse reviews can actually benefit from participating in a Groupon promotion. There are a couple of other studies that dispute the negativity of the selection effect. @ZhuEtAl19 shows that customers who received a discount leave more positive, albeit less informative, reviews. In an experimental study on Ebay, @CabralLi15 also finds that offering a rebate for leaving (any) review significantly decreases the likelihood of negative feedback. The effect is explained by clients reciprocating to the rebate, rather than byt the differences between customers buying with a rebate and without it. My study contributes to this debate by documenting the absence of a positive selection effect in a new market. Additionally, my paper is the first to focus on discrete changes in review tiers that follow the discounts, instead of studying the continuous effect of a discount on the review score.

Based on its findings, @ByersEtAl12 cautions businesses against running price promotions in an attempt to poach new customers and improve their online reputation. To the extent that managers and scholars perceive promotions to be an effective way of managing reputation, this finding presents a puzzle. A similar puzzle is encountered by @Zegners17, which argues that less-known authors of eBooks on a crowded online marketplace are more likely to give their books out for free in order to build reputation and escape the "zero reviews trap". While the idea is intuitive, the findings are that products employing free pricing are more likely to solicit *negative* feedback when sold for free, which somewhat undermines the strategy. I provide a novel mechanism--- the variance effect---that could explain the prevalence of price promotions when the selection effect of reviews is negative. The variance effect would explain the behavior observed in @Zegners17 as follows: if a  product with no reviews is already doomed, it would find it profitable to sell for free even if the probability to solicit favorable reviews is small. After all, sales can not fall below zero, but the upside of accumulating some positive reviews and escaping the trap is substantial. If this reasoning is commonplace, then the researcher would observe free pricing to deteriorate review scores, on average, but the average effect on sales would be positive.

The rest of this paper is organized as follows. Section \ref{dataSection} describes the institutional setting and the data I use. Section \ref{demandSection} develops and estimates the structural model of demand and gaming activity on Steam. The technical nature of the material in this section contributes greatly to its size, but the goal of this section is simply to quantify the importance of different review tiers on sales, and to show that discounts are effective in attracting new customers. The main findings are described in  Section \ref{descriptiveEvidence}. It opens with a stylized model of discounting for a product close to a review tier transition, and introduces the selection and the variance effects. The section proceeds by establishing that such discounting behavior takes place in the data. Section \ref{selectionEffect} supplements the demand model from Section \ref{demandSection} by a model of reviewing activity, and estimates its parameters in order to quantify the relative contributions of the selection and the variance effects to the observed patterns of discounting around review transitions. Section \ref{conclusion} concludes.

@@

Steam is arguably the largest online marketplace for selling computer games in the world. Founded in 2003, in 2013 it was responsible for about 75\% of PC games sold online globally [@steamBloomberg], and in 2017 it has earned around \$4.3 billion, with an estimated market share of 18\% in the entire market for PC games [@psgames]. Given an ongoing unprecedented growth in the size of the video games' market [\$43.4 billion 
in 2018, about the size of the U.S. film industry, @videoGamesMarket] and the increasing share of online sales in this market [83\% in 2018, compared to 20\% in 2009, @steamNPD[], Steam is a major player in an increasingly more important industry. Thus, this marketplace is not merely a laboratory for studies hoping to extrapolate the findings to other more well-known platforms, but is an important digital market to be studied in its own right.

Any user who owns a game on Steam can leave a review for that game. Starting from late 2016 Steam only uses reviews left by customers who have *purchased* the game in its review score calculation, excluding reviews left by customers who had obtained a key to activate the game through other channels (directly from the developer, or by purchasing the code from a different retailer). This distinguishes Steam from some other platforms studied in the literature, notably Yelp and TripAdvisor, where any user can leave a review (and, to a certain extent, Amazon, where non-verified users can also leave reviews). This gives me confidence in the authenticity of most reviews. This confidence is further backed by the importance of Steam to game developers and publishers, and Steam's history of monitoring the platform for fraudulent activity and excluding unscrupulous actors [@steamPurge]. With such high stakes, and a non-negligible risk of being caught, there are good reasons to expect the developers to behave scrupulously.

A review consists of a binary grade, "thumbs up" or "thumbs down", and review's text. A *review score* is defined as the fraction of positive reviews among all reviews a game has, provided it has at least 10 reviews. Based on the score, Steam assigns *review tiers* to each game\footnote{I use words “tier”, “bin”, and “label” interchangebly througout the text}. These labels\footnote{There are labels worse than “Negative”, but they are rare, so I bin all of them into “Negative”} and the mapping rules are summarized in Table \ref{tab:ReviewBinsTable}. For example, a game with 7 positive and 2 negative reviews would have neither a review score, nor a label, but an extra positive review would promote it to the “Positive” bin.

@@

Steam's homepage welcomes customers with a selection of featured games, that could include new games, popular games that are currently on a discount, games that have recently released a major update, etc. [@steamVisibility]. A customer could either click on the games already presented to her, or browse one of the categories that Steam offers. Available categories are based on games' characteristics such as performance (e.g., “Top Sellers”, “New Releases”), genre (e.g, “Racing”, "Anime", “Simulation”), or technical characteristics (VR or controller support). Games within a category are organized into a list, with an example session presented in Figure \ref{steamStore}. From that list the user can get some basic information about each title, such as its name, price, and if the game is currently on a discount. Importantly, if the user hovers her cursor over a game, she could further see the review label of the game and the number of reviews the game has. I use this feature of Steam's store to rationalize why later in the analysis I choose to focus on the review labels as my main explanatory review variables, rather than, say, the review score or the review texts. Granted, informative review texts could be important for purchase decisions [@ChevalierMayzlin06], but on Steam, in order to gain access to such information, a customer should be willing to click on the game in the first place. @deLanghe15 reports that consumers place an unreasonably high weight on the star rating of products\footnote{The title of the present study is an omage to the masterfuly chosen title of \citet{deLanghe15}.}. Thus, I conjecture that games with better review labels will, other things equal, attract more customers, and lead to more sales. Crucially, according to Steam's documentation, all review labels better than “Negative“ have a very similar contribution to visibility on the platform, which means, for example, that games are not ordered by their review labels when the customer is browsing different categories [-@steamVisibility2]. Therefore, any effect of the review labels on sales should come through the perceived quality differences between different bins, rather than some mechanical visibility differences. As an illustration, note that the first game in the list depicted in Figure \ref{steamStore} has “Mixed” reviews.

@@

Descriptive information on any game, that I will refer to as “static”, such as its title, developer, release date, etc., are readily available from Steam, and this information is also present on SteamDB. More importantly, Steam Database contains time series of prices and player activity for each game on Steam on a daily level. In principle, the pricing information could be obtained by a repeated scraping of the store. However, the player activity information is not trivial to obtain, as Steam does not directly reveal such data, let alone the data on sales of different titles. The creators of SteamDB have declined to explain their collection method, but their reputation in the gaming community most certainly implies that they are doing the best they can. The resulting variable that SteamDB offers, that I will refer to as the *player count*, measures the maximum number of concurrent players for each game on a daily basis. To clarify this definition, consider an example game that, on some day, was played by 10 people at every hour, except noon, when 13 people played the game simultaneously. The recorded player count for this game on that day will be 13. The price and the player count time series are the major “dynamic” variables used in the analysis. The last dynamic variable, namely the review score of each game, is obtained by scraping the reviews directly from Steam, and reverse engineering the evolution of the review score.

@@

The final sample includes `r info[, .N]` games which I observe for `r panel[, max(age), by = ID][, round(mean(V1))]` days each, on average. The main variables in the analysis are the aforementioned dynamic variables: player count, price, and review score. An example observation from the sample is given in Figure \ref{exampleGame}. For the majority of the games in the sample, the player count is the highest around the release date, and then it quickly fades away and oscillates around a smaller level. The player count also jumps when a discount is given, reflecting the influx of new players. Games differ a lot in their sizes, as is evident from Figure \ref{sampleSizeHist} (in the Appendix).

@@

As the goal of the paper is to understand if firms use pricing tools in order to improve their online reputation, a detailed overview of pricing and review variables is in order. A representative game in the sample never changes its price, but instead occasionally goes on discounts, slowly increasing their magnitude as the game ages. There are `r panel[discount==F, diff(price), by = ID][V1>0, .N]` incidents of price change in the data, compared to 
`r panel[discNew==T, .N]` discounts. Steam has a number of rules that regulate price promotions on its platform. A game can have a launch discount, but, otherwise, it has to wait for two months since the release before changing its price or giving a discount. A game can not go on discounts too frequently, and has to wait between four to six weeks after a price promotion to be able to run a new one. The duration of a custom discount is restricted to be at least one full day, and at most two weeks. Besides these custom discounts, that are fully managed by the firms, Steam has a series of curated discounts, when the platform invites selected titles to go on a discount. As @steamDiscounting explains it, “while there aren't strict rules, as a base guideline we tend to focus on the top 10-20% selling games on Steam that are positively reviewed and have otherwise proven to be successful”. Curated promotions are featured prominently on Steam's main page, and, arguably, lead to more visibility and sales for the participating titles than custom discounts, which also contribute to visibility, but typically do not get the front-page promotional slots. An important type of curated discounts are the so-called “Seasonal Sales”---big platform-wide events that take place about four times a year around major holidays. Figure \ref{seasonalSalesPeriods} (in the Appendix) shows that the biggest sales take place in Winter (Christmas and New Year) and Summer (July 4), but there are also significant discounts in the Fall (Halloween and Thanksgiving). Around `r  round(panel[discSeason==T & discNew == T, .N]/panel[discNew==T, .N]*100)`% of discounts in the sample go live during a Seasonal Sale. Thus, firms have significant agency when it comes to running price promotions, but platform regulations and platform-wide discounts are important determinants of firms' decision to discount.

The path of the review score of a typical game is quite different from its price history, in that the review score tends to settle quickly. Recall that the review score is just the fraction of positive reviews among all reviews, so the law of large number implies that this ratio crystallizes as more reviews flow in. Second plot in Figure \ref{reviewDescriptivePlots} shows that games tend to receive half of the reviews they have at the age of 180 days in their first month after the release. On average across games, the standard deviation of the review score over time is just `r round(panel[, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)`  (out of one hundred), with a split of `r round(panel[age <= 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` in the first thirty days and `r round(panel[age > 30, sd(score, na.rm=T), by = ID][, mean(V1, na.rm = T)], 2)` after that. Given how little the review score changes after the first month, the distribution of games by bins at the age of 180 days, depicted in Figure \ref{reviewDescriptivePlots}, should be representative of the situation at other ages.
